Heuristics and Really Hard Instances for Subgraph Isomorphism Problems

### 2016-04-18 paper/paper.tex
Include Glucose plots

The pseudo-boolean (PB) encoding is as follows. For each pattern vertex $v$ and each target vertex
$w$, we have a binary variable which takes the value 1 if and only if $v$ is mapped to $w$.
Constraints are added to ensure that each pattern vertex maps to exactly one target vertex, that
each target vertex is mapped to by at most one pattern vertex, that adjacent vertices are mapped to
adjacent vertices, and that non-adjacent vertices are mapped to non-adjacent vertices. We used the
Clasp solver~\citep{gekakaosscsc11a} version 3.1.3 to solve the pseudo-boolean instances.  The
instances that are hard for the Glasgow solver remain hard for the PB solver, including instances
inside the central region, and the easy satisfiable instances remain easy. (Similar results were
seen with the Glucose SAT solver using a direct encoding of the cardinality constraints. We also
implemented an integer program encoding; the Gurobi solver was only able to solve some of the
trivial satisfiable instances, and was almost never able to prove unsatisfiability within the time
limit.)

>>>>

The pseudo-boolean (PB) encoding is as follows. For each pattern vertex $v$ and each target vertex
$w$, we have a binary variable which takes the value 1 if and only if $v$ is mapped to $w$.
Constraints are added to ensure that each pattern vertex maps to exactly one target vertex, that
each target vertex is mapped to by at most one pattern vertex, that adjacent vertices are mapped to
adjacent vertices, and that non-adjacent vertices are mapped to non-adjacent vertices. We used the
Clasp solver~\citep{gekakaosscsc11a} version 3.1.3 to solve the pseudo-boolean instances.  The
instances that are hard for the Glasgow solver remain hard for the PB solver, including instances
inside the central region, and the easy satisfiable instances remain easy. Similar results were
seen with the Glucose SAT solver \cite{glucose} using a direct encoding of the cardinality constraints. (We also
implemented an integer program encoding; the Gurobi solver was only able to solve some of the
trivial satisfiable instances, and was almost never able to prove unsatisfiability within the time
limit.)
